biclaR

### 2024-12-05 code/biclarwww/index.Rmd
insert video 2 and 3

### Parte II: Como usar o biclaR?

(*comming soon!*)

>>>>

### Parte II: Como usar o biclaR

<div align="center"><iframe width="1000" height="563" src="https://www.youtube.com/embed/PPZMcD0MrZI" title="YouTube video player" frameborder="0" data-external="1" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe></div>

### Parte III: Como ler os ficheiros e fazer análises em SIG

<div align="center"><iframe width="1000" height="563" src="https://www.youtube.com/embed/d1wu1Rpl5y8" title="YouTube video player" frameborder="0" data-external="1" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe></div>
